Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-05 paper-webserver.tex
ADD: basic outline for graph dbs and web design

\title{Article title}

@@

\section{MATERIALS AND METHODS}
% outline
% para
% problem: predictive analylitcs in minutes - sol'n: RQ
%	related: packaging of modules in conda
% para (probably 2 paras)
% problem: distribute tasks & automate installation - sol'n: docker
% para(probably 2 for graphs)
% problem: storage up 10,000+ genomes - sol'n: graph database
% para
% problem: responsive ui that's easy to navigate - sol'n: react & material design
% shortpara
% problem: CI/testing - sol'n Github, TravisCI, Pytest

We present Spfy as an integrated predictive genomics toolkit for pathogens / \textit{E. coli} which leverages advances in web application development and deployment.

which our analysis modules rely on.

These changes enable real-time genome analysis and database storage of results for upwards of 5000 genomes.

@@

\subsection{Graph databases and ontologies}

\subsection{Intuitive web design}

@@

\section{RESULTS}

@@

\section{DISCUSSION}

\subsection{Discussion subsection one}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text.

\subsection{Discussion subsection two}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

\subsection{Discussion subsection three}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text.

>>>>

\title{Spfy: distributed predictive genomics of E.coli with graph based result linkage}

@@

\section{METHODS AND IMPLEMENTATION}
% outline
% para
% problem: predictive analylitcs in minutes - sol'n: RQ
%	related: packaging of modules in conda
% para (probably 2 paras)
% problem: distribute tasks & automate installation - sol'n: docker
% para(probably 2 for graphs)
% problem: storage up 10,000+ genomes - sol'n: graph database
% para
% problem: responsive ui that's easy to navigate - sol'n: react & material design
% shortpara
% problem: CI/testing - sol'n Github, TravisCI, Pytest

% Inputs: more like going from file -> analysis -> graph db (not a hard subsection)
Spfy takes assembled genomes as input, runs selected analyses modules, and converts the results into a graph structure for upload.

% Outputs: more like what we query from blazegraph and how we use it (not a hard subsection)
Spfy queries the graph database to run analyses XYZ and build visualizations.

\subsection{Graph databases and ontologies}
% para
% 1. spfy is built around graph technologies
% 2. graph dbs store data as a series of links
% 3. existing graph dbs and bioinformatics implementations
% para
% 1. how we structure our graph
% 2. ontoogies used
% 3. inferencing
% 3 1/2. SPARQL queries
% 4. results/timings

\subsection{Web design}
% para
% 1. goals: intuitive/familar, ease of use 
% 2. design specs and different examples
% 3. Google Material design
% 4. some focus on card based design
% para
% 1. implementation: reactjs, react-md, ES6, JSX
% 2. A to B: example of how users go from uploading files to results
% 3. backwards compatibility with older browsers: transpile via Babel
% 4. separation from Flask layer

@@

@@

\subsection{Guides and documentation}

\section{RESULTS AND DISCUSSION}

@@
